\documentclass[11pt]{article}
\usepackage{fontspec}
\usepackage{libertine}
\usepackage[margin=0.75in]{geometry}
\usepackage{xcolor}
\usepackage{url}
\usepackage{hyperref}

\setmainfont{Liberation Sans}

\pagestyle{empty}

\begin{document}

\noindent \textbf{AMAN KUMAR} \\
Vancouver, BC \ $\cdot$ \href{amankumar7111@outlook.com}{amankumar7111@outlook.com} \ $\cdot$ \href{linkedin.com/in/aman1776}{linkedin.com/in/aman1776} \ $\cdot$ (236) 885-2285 \hfill Date: 25/06/2026

\vspace{8pt}
\hrule height 0.5pt\relax
\vspace{8pt}

\noindent \textbf{Hiring Committee} \\
RAM Consulting \\
700-409 Granville St. \\
Vancouver, BC V6C 1T2

\vspace{8pt}
\noindent \textbf{Re: Senior Project Manager --- Expression of Interest}

\vspace{6pt}
Dear Hiring Committee,

\vspace{4pt}
RAM's tagline is ``Your Project. Our Passion.'' That's the phrase that stopped me on your homepage --- because it's the same philosophy I brought to every project I led for 8 years. I am writing to express my interest in the Senior Project Manager Expression of Interest at RAM Consulting.

\vspace{4pt}
Here's what I built, and why it maps to what RAM does:

\vspace{4pt}
I joined a multi-site healthcare organization as one of three founding operators. When I left, it was 70 people across 32 locations with a \$17M acquisition that I directed end-to-end. The project delivery infrastructure I built --- from technology transformation to P\&L management to cross-functional coordination across 12 departments --- gave the organization the operational backbone to scale without breaking.

\vspace{4pt}
My most direct parallel to RAM's work: I directed an 8-workstream acquisition simultaneously. I coordinated 20+ external advisors (legal, financial, operational). I managed the integration across all 32 locations within 90 days. I retained 100\% of key talent. I delivered the project on time and on terms. That's what project delivery means --- not a slide deck, but a completed outcome.

\vspace{4pt}
What I also know: RAM embeds with clients in sectors I respect --- marine, transportation, utilities, energy. These are complex, multi-stakeholder environments where the margin for error is thin and the payoff for excellent delivery is enormous. My healthcare background is analogous: I coordinated across health authorities, insurance providers, and regulatory bodies. I managed risk, quality, and schedule constraints simultaneously. I presented to boards, not just internal teams.

\vspace{4pt}
I am based in Vancouver and available for immediate start. I hold an MBA and bring 8 years of progressive project delivery experience --- including P\&L ownership, technology transformation, and multi-stakeholder coordination at scale. I am authorized to work in Canada.

\vspace{4pt}
I would welcome the opportunity to discuss how my background in complex project delivery can contribute to RAM's infrastructure and energy project portfolio. Thank you for your time and consideration.

\vspace{8pt}
Best regards, \\
\textbf{AMAN KUMAR} \\
Phone: (236) 885-2285 \\
Email: \href{amankumar7111@outlook.com}{amankumar7111@outlook.com} \\
LinkedIn: \href{linkedin.com/in/aman1776}{linkedin.com/in/aman1776}

\end{document}