\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{fontspec}
\usepackage[margin=0.75in]{geometry}
\usepackage{microtype}

% UBC Cover Letter -- Liberation Sans 11pt, 0.75in margins

\setmainfont{Liberation Sans}
\geometry{margin=0.75in}

\begin{document}

Aman Kumar \\
+1 236-885-2285 \textbar\ amankumar7111@outlook.com \textbar\ LinkedIn: linkedin.com/in/aman1776 \\
Vancouver, BC \\[12pt]

June 25, 2026 \\[12pt]

UBC Human Resources \\
University of British Columbia \\
Vancouver, BC \\[12pt]

\textbf{Re: Senior Manager, Strategic Initiatives and Engagement} \\[8pt]

Dear Hiring Committee, \\[8pt]

UBC's Shaping UBC's Next Century plan articulates an ambitious mandate: deliver strategic priorities through disciplined resource allocation, stakeholder engagement, and institutional effectiveness. The Senior Manager, Strategic Initiatives and Engagement role sits at the center of this mandate. This is exactly where I deliver the most value. \\[8pt]

I spent eight years building the strategic and operational infrastructure for a multi-site organization from scratch. When I joined, there were 3 people, no governance structure, and no strategic planning process. When I left, it was 70 people across 32 locations with a \$17M acquisition that I directed end-to-end. The strategic planning system I built --- annual strategy sessions cascading through departmental OKRs, board-level reporting, and quarterly performance reviews --- gave executive leadership real-time visibility into execution across every location. The budget frameworks I designed governed resource allocation across 12 departments. The acquisition I led involved 8 concurrent workstreams and an integration that retained 100\% of key talent. \\[8pt]

What made this possible was not a pre-existing playbook. I created it --- the governance rhythms, the strategic planning cycles, the financial models, the stakeholder engagement frameworks, the policy documentation systems --- all from scratch, across a complex, multi-jurisdictional operating environment. I learned that strategic leadership in complex institutions is not about having all the answers. It is about building the process that surfaces the right questions, engages the right stakeholders, and delivers the right outcomes. \\[8pt]

UBC faces exactly the challenges I have solved: how to allocate constrained resources across competing strategic priorities, how to align diverse stakeholders around shared goals, how to build governance frameworks that satisfy both institutional accountability and external transparency, how to translate strategic intent into operational reality across a large, complex organization. I have navigated this complexity in healthcare. I am ready to navigate it at UBC. \\[8pt]

I am drawn to UBC because it is the intellectual backbone of British Columbia's future. I want to contribute to that future as someone who builds --- not as an observer, but as a practitioner who has delivered strategic infrastructure at scale. My MBA, my 8 years of progressive operational leadership, and my \$17M acquisition experience have prepared me to do exactly what this role requires. \\[8pt]

I would welcome the opportunity to discuss how my experience building strategic and operational infrastructure can support UBC's next chapter of academic excellence and institutional impact. \\[12pt]

Sincerely, \\[8pt]

Aman Kumar

\end{document}