\documentclass[11pt]{article}
\usepackage{fontspec}
\usepackage{libertine}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{url}
\usepackage{setspace}

\setmainfont{Liberation Sans}

\geometry{top=0.75in, bottom=0.75in, left=0.75in, right=0.75in}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\begin{document}

\textbf{AMAN KUMAR}\\[4pt]
+1 236-885-2285  |  amankumar7111@outlook.com  |  linkedin.com/in/aman1776\\
Vancouver, BC, Canada\\[12pt]

Date: 25/06/2025\\[12pt]

Practice Better\\
Toronto, ON (Remote Canada)\\[12pt]

\textbf{Re: Director of Revenue Operations}\\[12pt]

Dear Hiring Manager,\\[8pt]

I build revenue operations infrastructure. I've done it from zero, scaled it to \$4M ARR, and delivered a
\$17M exit. That's the exact journey Practice Better is on right now --- and I want to be the operator who
builds what comes next.\\[8pt]

When I joined SkyflyMD, there was no revenue operations system. No billing infrastructure, no scheduling
automation, no KPI visibility. By the time I directed the \$17M exit, we had a complete revenue operations
stack spanning 32 locations: EHR, billing, RCM, analytics, and forecasting --- all built in-house, all
scaled from zero to support 70 employees and \$4M ARR. I didn't inherit a system. I built one.\\[8pt]

What makes this relevant to Practice Better is what I learned building that system: in healthcare SaaS, revenue
operations is not just about pipeline management. It's about aligning clinical workflows with financial
outcomes --- making sure the GTM engine and the product engine speak the same language. That's the gap I've
seen most scaling healthcare SaaS companies struggle with, and that's exactly what I've solved.\\[8pt]

At SkyflyMD, I also managed the full P\&L --- \$4M ARR across 12 departments. I built the forecasting models,
the variance analysis frameworks, and the board-level reporting that gave executive leadership real-time
visibility. I know what it means to own the numbers and be accountable for them.\\[8pt]

I'm targeting Director of Revenue Operations roles at scaling healthcare SaaS companies because this is the
exact problem I've already solved. Practice Better is at the stage where the founder can't own revenue ops
alone anymore --- and that's where I come in. I build the function, hire the team, and create the
infrastructure that makes the next phase of growth inevitable.\\[8pt]

I would welcome the opportunity to discuss how my experience building and scaling revenue operations for
healthcare SaaS can support Practice Better's next chapter.\\[12pt]

Best regards,\\[12pt]
\textbf{AMAN KUMAR}\\[4pt]
Phone: +1 236-885-2285\\[4pt]
Email: amankumar7111@outlook.com\\[4pt]
LinkedIn: linkedin.com/in/aman1776\\

\end{document}